%%
%% This is file `ledeasy.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% ledmac.dtx  (with options: `easy')
%% 
%%   Author: Peter Wilson (Herries Press) herries dot press at earthlink dot net
%%   Copyright 2003 -- 2005 Peter R. Wilson
%% 
%%   This work may be distributed and/or modified under the
%%   conditions of the LaTeX Project Public License, either
%%   version 1.3 of this license or (at your option) any
%%   later version.
%%   The latest version of the license is in
%%      http://www.latex-project.org/lppl.txt
%%   and version 1.3 or later is part of all distributions of
%%   LaTeX version 2003/06/01 or later.
%% 
%%   This work has the LPPL maintenance status "author-maintained".
%% 
%%   This work consists of the files listed in the README file.
%% 
\documentclass{article}
\usepackage{ledmac}
%% number every line
\setcounter{firstlinenum}{1}
\setcounter{linenumincrement}{1}
%% Show some B series familiar footnotes, lettered and paragraphed
\renewcommand*{\thefootnoteB}{\alph{footnoteB}}
\footparagraphX{B}
%% no endnotes
\noendnotes
%% narrow sidenotes
\setlength{\ledrsnotewidth}{4em}
\title{Simple Example}
\author{Peter Wilson\thanks{Standing on the shoulders of giants.}}
\date{}
\begin{document}
\maketitle
\tableofcontents
\section{First}
   This is a simple example of using the \textsf{ledmac}
package with ordinary LaTeX constructs.

\subsection{Example text}\label{subsec}

\beginnumbering
\pstart
The \textsf{ledmac} package lets you do some unusual things in
a LaTeX document. For example you can have lines numbered and
there are
\edtext{several}{\Afootnote{This is an `A' footnote.}}
\edtext{levels}{\Bfootnote{This is a `B' level footnote.}}
of footnotes.
You can label lines within the numbered text and refer to them
outside. Do not try and use any normal LaTeX
marginpars\footnote{You will get a warning but no text.}%
\ledrightnote{Sidenotes are OK}
or \edtext{exotica}{\Afootnote{Like floats.}}
within the numbered portions of the text\edlabel{line}.
\pend
\endnumbering

\section{Last}

    I forgot to mention that you can use ordinary
footnotes\footnote{An ordinary footnote}\footnote{And another}
outside the numbered text. You can also\footnoteB{Additionally}
have\footnoteB{Specify} formatted footnotes\footnoteB{Like this}
in normal\footnoteB{Text that does not have line numbers} text.

   There are \lineref{line} numbered lines in the example shown
in section~\ref{subsec}.

\end{document}
\endinput
%%
%% End of file `ledeasy.tex'.
