%%
%% This is file `ledioc.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% ledmac.dtx  (with options: `ioc')
%% 
%%   Author: Peter Wilson (Herries Press) herries dot press at earthlink dot net
%%   Copyright 2003 -- 2005 Peter R. Wilson
%% 
%%   This work may be distributed and/or modified under the
%%   conditions of the LaTeX Project Public License, either
%%   version 1.3 of this license or (at your option) any
%%   later version.
%%   The latest version of the license is in
%%      http://www.latex-project.org/lppl.txt
%%   and version 1.3 or later is part of all distributions of
%%   LaTeX version 2003/06/01 or later.
%% 
%%   This work has the LPPL maintenance status "author-maintained".
%% 
%%   This work consists of the files listed in the README file.
%% 
%% ledioc.tex
\documentclass{article}
\usepackage{ledmac}

 \noendnotes
 \makeatletter

 \newcommand{\os}{\scriptsize}
 \setcounter{firstsublinenum}{1000}
 \frenchspacing \setlength{\parskip}{0pt} \hyphenpenalty=1000

 % Say \nolinenums if you want no line numbers in the notes.
 \newif\ifnolinenums
 \newcommand{\nolinenums}{\global\nolinenumstrue}
 \newcommand{\linenums}{\global\nolinenumsfalse}

 \renewcommand{\rightlinenum}{\ifbypage@\ifnum\line@num<10\kern.5em\fi\else
 \ifnum\line@num<10\kern1em\else\ifnum\line@num<100
   \kern.5em\fi\fi\fi\kern.5em\numlabfont\the\line@num
   \ifnum\subline@num>0:\the\subline@num\fi}

 \renewcommand{\leftlinenum}{\numlabfont\the\line@num
   \ifnum\subline@num>0:\the\subline@num\fi \kern.5em}
 \linenummargin{outer}
 \lineation{page}

 \newcommand{\ggfootfmt}[3]{%
   \notefontsetup
   \let\par=\endgraf
   \rightskip=0pt \leftskip=0pt
   \setlength{\parindent}{0pt} \parfillskip=0pt plus 1fil
   \ifnolinenums\relax\else
     \begingroup \os \printlines#1|\endgroup
     \enskip
   \fi
   {\rmfamily #2\def\@tempa{#2}\ifx\@tempa\empty
     \else]\enskip\fi#3\penalty-10 }}

 % Now reset the \Afootnote parameters and macros:
 \footparagraph{A}
 \let\Afootfmt=\ggfootfmt
 \dimen\Afootins=\vsize
 \skip\Afootins=3pt plus9pt
 \newcommand*{\ggfootstart}[1]{\vskip\skip\Afootins}
 \let\Afootstart=\ggfootstart

 \newcommand*{\stage}[1]{\pstart\startsub\parindent=0pt
   \hangindent=3em\hangafter=0
   {\itshape #1}\let\par=\finishstage}
 \newcommand{\finishstage}{\pend\endsub}
 \newcommand{\sen}{\leavevmode\lower1ex\hbox{\textrm{''}}}
 \newcommand{\senspeak}[1]{\pstart\obeylines\setbox0=\hbox{\textrm{''}}%
   \leavevmode
   \lower1ex\copy0\kern-\wd0\hskip1em{\textit{#1}}%
   \hbox to1ex{}\ignorespaces}
 \newcommand*{\speak}[1]{\pstart\obeylines\hskip1em{\textit{#1}}%
   \hbox to1ex{}\ignorespaces}
 \def\nospeaker{\parindent=0em\pstart\let\par=\pend}
 \newcommand*{\nospeak}{\pstart\obeylines}
 \makeatother

\begin{document}

 \setlength{\parindent}{0pt}

 \beginnumbering

 \stage{Oedipus \edtext{entreth}{\Afootnote{\textit{intrat} MS}}.}

 \nospeak
 Or that with wrong the right and doubtlesse heire,
 Shoulde banisht be out of his princely seate.
 Yet thou O queene, so fyle thy sugred toung,
 And with suche counsell decke thy mothers tale,
 That peace may bothe the brothers heartes inflame,
 And rancour yelde, that erst possest the same.
 \pend

 \speak{Eteocl.} Mother, beholde, youre hestes for to obey,
 In person nowe am I resorted hither:
 In haste therefore, fayne woulde I knowe what cause
 With hastie speede, so moued hath your mynde
 To call me nowe so causelesse out of tyme,
 When common wealth moste craues my onely ayde:
 Fayne woulde I knowe, what queynt commoditie
 Persuades you thus to take a truce for tyme,
 And yelde the gates wide open to my foe,
 The gates that myght our stately state defende,
 And nowe are made the path of our decay.
 \pend

 \senspeak{Ioca.}Represse deare son, those raging stormes of wrath,
 \sen That so bedimme the eyes of thine intente,
 \edtext{\sen As when \edtext{the}{\Afootnote{thie MS}} tongue %
   (a redy Instrument)
 \sen Would \edtext{fayne pronounce}{\Afootnote{faynest tell MS}} %
   the meaning of \edtext{the minde}{\Afootnote{thy minde MS}},
 \sen \edtext{It}{\lemma{It \dots\ worde.}\Afootnote{Thie %
   swelling hart puft vp with wicked ire / Can scarce pronounce %
   one inward louing thought. MS}} cannot speake one honest %
   seemely worde.}{\lemma{As \dots\ worde.}\Afootnote{\textit{not %
   in} \os73}}
 \sen But when disdayne is shrunke, or sette asyde,
 \sen And mynde of man with leysure can discourse
 \sen What seemely woordes his tale may best beseeme,
 \sen And that the toung vnfoldes without affectes
 \sen Then may proceede an answere sage and graue,
 \sen And euery sentence sawst with sobernesse:
 Wherefore vnbende thyne angrie browes deare chylde,
 And caste thy rolling eyes none other waye,
 That here doost not \edtext{\textit{Medusaes}}{%
 \Afootnote{One of the furies. {\os75}m}} face beholde,
 But him, euen him, thy blood and brother deare.
 And thou beholde, my \textit{Polinices} eke,
 Thy brothers face, wherin when thou mayst see
 Thine owne image, remember therwithall,
 That what offence thou woldst to him were done,
 \pend
 \endnumbering

\end{document}

\endinput
%%
%% End of file `ledioc.tex'.
